Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-27 edubots_surveys.Rnw
Fixing table unsuccessfully
Add latest papers (2021) and include them in SoA :memo: #6

% The Use of Chatbots in Higher Education
The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually well where synchronous conversations take place. 
% Antonio - I cannot understand this sentence... what's the point of the expression 'usually well'?
The use of conversational agents (chatbots) in higher education is
still at its infancy \cite{yang2019opportunities}. Nevertheless,
recent studies examining their positive impact on students' academic
performance \cite{perez2020rediscovering} and engagement
\cite{differ.chat,abbas2021onlinechat} have led to a growing interest
in using this technology in the (possibly virtual) classroom. Indeed, the use of chatbots in
collecting course feedback from students in higher education improved
students' response quality and boosted their enjoyment levels
\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using
either tools such as mobile devices or teaching strategies based on
gamification \cite{Yildirim2017} can improve student motivation. In
this sense, the authors in \cite{Pimmer2019} carried out a series of experiments with
technological tools whose results showed positive perception and
acceptance of the use of technology in teaching and learning.

@@

Regarding the factors for the adoption of chatbots in higher
education, many studies have focused on the evaluation of technology
acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
higher education is a special domain where according to Hobert \cite{hobert2019you}, 
specific pedagogical factors such as learning success or increased motivation are more important.  
Therefore, to develop efficient chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) expectations needs to be
carefully collected and taken into consideration
\cite{sjostrom2018designing,tsivitanidouusers}.

Along this line of work, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard, whereas the present study is focused on the other key actor in this challenge, i.e. educators.

@@

To provide a different perspective another analysis was carried out using models from the field of machine learning. The idea was to be able to identify which features measured in the survey could identify willingness to change. As chatbots are an emerging technology, it is quite probable that this new change will come sooner than later considering the improvemente in Virtual and Augmented Reality \cite{}.

@@

\begin{table}
\begin{tabular}{|c|c|c|c|c|}
\hline
\# Variable & Name & MI (considering one variable) & Max Relevance & mRMR\\
\hline
0 & AgendaBot	&  &  &\\
1 & ClassMaterialBot &	&  &	\\
2 & Age	&		&  &  \\
3 & Experience &			&  &  	\\
4 & FAQBot &			&  &  	\\
5 & GradesBot &			&  &  	\\
6 & Gender &			&  &  	\\
7 & MessagingPlatform0ne &			&  &  	\\
8 & MessagingPlatformOther &			&  &  	\\
9 & MessagingPlatformProvided	&			&  &  \\
10 & MessagingPlatformSlack	&			&  &  \\
11 & MessagingPlatformTelegram	&			&  &  \\
12 & MessagingPlatformWhatsApp	&			&  &  \\
13 & OtherBot	&			&  &  \\
14 & Sector	&			&  &  \\
15 & Messaging Organization $\rightarrow$ Number of approaches considered	&			&  &  \\
16 & Degrees $\rightarrow$ Number of degrees involved	&			&  &  \\
17 & Discipline	&		&  &  	\\
\hline
% Output & \multirow{3}{PostCOVID changes} & 	\\
\hline
\end{tabular}
\caption{Mapping of feature numbers to survey questions.}
\label{tab:feature_results}
\end{table}

>>>>

% The Use of Chatbots in Higher Education
The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually dwell in systems where synchronous conversations take place. 
% Antonio - I cannot understand this sentence... what's the point of the expression 'usually well'?
% Dwell, not well - JJ
The use of conversational agents (chatbots) in higher education is
still at its infancy \cite{yang2019opportunities}. Nevertheless,
recent studies examining their positive impact on students' academic
performance \cite{perez2020rediscovering} and engagement
\cite{differ.chat,abbas2021onlinechat} have led to a growing interest
in using this technology in the (possibly virtual) classroom. Indeed, the use of chatbots in
collecting course feedback from students in higher education improved
students' response quality and boosted their enjoyment levels
\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using
either tools such as mobile devices or teaching strategies based on
gamification \cite{Yildirim2017} can improve student motivation. In
this sense, the authors in \cite{Pimmer2019} carried out a series of experiments with
technological tools whose results showed positive perception and
acceptance of the use of technology in teaching and learning.

@@

Regarding the factors for the adoption of chatbots in higher
education, many studies have focused on the evaluation of technology
acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
higher education is a special domain where, according to Hobert \cite{hobert2019you}, 
specific pedagogical factors such as learning success or increased motivation are more important.  
Therefore, to develop efficient chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) expectations needs to be
carefully collected and taken into consideration
\cite{sjostrom2018designing,tsivitanidouusers}.

Along this line of work, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard, whereas the present study is focused on the other key actor in this challenge, i.e. educators. This has been analyzed very recently by Chocarro et al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created a {\em technology acceptance model} that proposed a series of features that would make chatbots easier to accept; among them, formality of language as well as easiness and usefulness. The survey targeted primary and secondary education teachers, and was also more interested in the general use of chatbots in education, not specifically in a classroom setting, seeking educational outcomes. However, they establish a series of results that are obviously interesting and relevant for this work.

We will present next the methodology we have followed to find out teachers' attitudes.

@@

To provide a different perspective another analysis was carried out using models from the field of machine learning. The idea was to be able to identify which features measured in the survey could identify willingness to change. As chatbots are an emerging technology, it is quite probable that this new change will come sooner than later considering the improvements in Virtual and Augmented Reality \cite{}.

@@

\begin{table}
\begin{tabular}{|c|c|c|c|c|}
\hline
\# Variable & Name & MI (considering one variable) & Max Relevance & mRMR\\
\hline
0 & AgendaBot	&  &  &\\
1 & ClassMaterialBot &	&  &	\\
2 & Age	&		&  &  \\
3 & Experience &			&  &  	\\
4 & FAQBot &			&  &  	\\
5 & GradesBot &			&  &  	\\
6 & Gender &			&  &  	\\
7 & MessagingPlatform0ne &			&  &  	\\
8 & MessagingPlatformOther &			&  &  	\\
9 & MessagingPlatformProvided	&			&  &  \\
10 & MessagingPlatformSlack	&			&  &  \\
11 & MessagingPlatformTelegram	&			&  &  \\
12 & MessagingPlatformWhatsApp	&			&  &  \\
13 & OtherBot	&			&  &  \\
14 & Sector	&			&  &  \\
15 & Messaging Organization $\rightarrow$ Number of approaches considered	&			&  &  \\
16 & Degrees $\rightarrow$ Number of degrees involved	&			&  &  \\
17 & Discipline	&		&  &  	\\
\hline
Output & \multicolumn{3}{c}{PostCOVID changes} & 	\\
\hline
\end{tabular}
\caption{Mapping of feature numbers to survey questions.}
\label{tab:feature_results}
\end{table}
